### 2019-07-05 manuscript.tex
Update manuscript.tex

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx and xxx  respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

=====stop reading===

@@

Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly, and \%, \%, \% and \%  of the samples thought FGC should continue as well.

The results of the three models are at figure?.  The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and FGC prevalence in a community; so as the following factors:  country, media, education, age and religion and the community levels of media, education.  We did not find clear association of the community level of beliefs of fgc benefits and the three responses.

@@

Tables and figures to be included:
- table of basic sociodemographic results
- 3 figures of the results of the 3 models
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% a chart like figure 8-8D \cite{UNIC13}

>>>>

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the mixed structure (daugher_ persistence) model, while the persistence model included all the women in the samples; and that resulted in xxx, xxx, xxx and xxx, and 7861, 13071, 18311 and 7253 respectively.  \cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

@@

\cf{We need to show both isoplots and effect plots because some binary variables are not on the isoplots.}

Baseline socio-demographic and sample characteristics are shown in figure x.  The prevalence of FGC are 31.8\%, 88.6\%, 45.9\% and 91.0\%, and 15.5\%, 73.9\%, 20.6\% and 65.5\% of the samples thought FGC should be continued in Kenya, Mali, Nigeria and Sierra Leon accordingly.

The results of the three models are at figure?.  The findings showed that women’s fgc status, beliefs of fgc benefits and FGC prevalence were all clearly and positively associated with the two responses (intention to cut daughters, attitudes on whether FGC should be continued); so as the following factors but in negative association:  country, media, education, age and religion and the community levels of beliefs of FGC benefits \cf{this one is tricky to interpret}.  The association of gender awareness with the two responses was not clear in our findings both at a population \cf{or individual} and a community level.

===== stop reading =======

@@

Tables and figures to be included:
- a figure of women’s FGC prevalence vs. their intention of cutting daughters vs. attitudes towards FGC continuity.  (ref to \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3302551/}, Fig 1)
% figure:  plots of FGC benefits (This figure will be important. It tells us what women thinks about why FGC).
% figure: to put the first PCA of FGC believes of the 4 nations at the community level and maybe in one figure
% a chart like figure 8-8D \cite{UNIC13}
